---
title: "Diagnostic Plots"
subtitle: "The effects of supervision upon effort during resistance training: A Bayesian analysis of prior data and an experimental study of private strength clinic members"
author: "James Steele, James Fisher, Tim Dettmann"
format:
  pdf:
    documentclass: report
    toc: false
    number-sections: false
    highlight-style: github
    fig-width: 10
    fig-height: 10
---
```{r,message=FALSE,warning=FALSE,echo=FALSE}
targets::tar_config_set(store = here::here('_targets'))

```


# Prior Sample Models

## Time Under Load

### $\hat{R}$

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(rhat_prior_sample_tul)

rhat_prior_sample_tul

```

### Trace plots

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(trace_plot_prior_sample_tul)

trace_plot_prior_sample_tul

```

### Posterior predictive check

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(pp_check_prior_sample_tul)

pp_check_prior_sample_tul

```

## Rating of Perceived Effort

### $\hat{R}$

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(rhat_prior_sample_rpe)

rhat_prior_sample_rpe

```

### Trace plots

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(trace_plot_prior_sample_rpe)

trace_plot_prior_sample_rpe

```

### Posterior predictive check

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(pp_check_prior_sample_rpe)

pp_check_prior_sample_rpe

```

# Experimental Study Models

## Time Under Load

### $\hat{R}$

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(rhat_tul)

rhat_tul

```

### Trace plots

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(trace_plot_tul)

trace_plot_tul

```

### Posterior predictive check

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(pp_check_tul)

pp_check_tul

```

## Rating of Perceived Effort

### $\hat{R}$

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(rhat_rpe)

rhat_rpe

```

### Trace plots

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(trace_plot_rpe)

trace_plot_rpe

```

### Posterior predictive check

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(pp_check_rpe)

pp_check_rpe

```

## Rating of Perceived Discomfort

### $\hat{R}$

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(rhat_discomfort)

rhat_discomfort

```

### Trace plots

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(trace_plot_discomfort)

trace_plot_discomfort

```

### Posterior predictive check

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(pp_check_discomfort)

pp_check_discomfort

```
